\documentclass[10pt,a4paper,withhyper]{altacv}

\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

\usepackage{paracol}

\iftutex
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  \renewcommand{\familydefault}{\sfdefault}
\fi

\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelRed}{HTML}{450808}
\definecolor{PastelRed}{HTML}{8F0D0D}
\definecolor{GoldenEarth}{HTML}{E7D192}
\colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkPastelRed}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{PastelRed}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}

\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}

\begin{document}

\name{Chan-Ho, Im}
\tagline{Team Leader, DX Innovation Department}

\personalinfo{%
  \email{hala2517@gmail.com}
  \phone{+82-10-4621-4710}
  \location{Eumseong-gun, Chungcheongbuk-do, Republic of Korea}
  \github{hala2517}
}

\makecvheader

\columnratio{0.6}

\begin{paracol}{2}

%% ---- LEFT COLUMN ----

\cvsection{Experience}

\cvevent{Team Leader, DX Innovation Dept.}{Cosmecca Korea Co., Ltd.}{Jun 2016 -- Present}{Eumseong-gun, Chungcheongbuk-do}
\begin{itemize}
  \item Overseeing company-wide DX \& AX initiatives, on-site improvement activities (TPS), and cost reduction efforts.
  \item Leading 7 Task Force Teams (TFT) across departments to drive manufacturing innovation and digital transformation.
  \item \textbf{Achieved a 30\% increase in productivity} and a \textbf{20\% reduction in customer complaints}.
  \item \textbf{Realized 8 billion KRW in cost savings} for fiscal year 2025.
\end{itemize}

\cvsection{Capstone Design Project}

\cvevent{YOLO-based Video AI for Automated Line-of-Balance (LOB) Analysis in Manufacturing Packaging Processes}{Sungkyunkwan University -- Dept. of Smart Factory Convergence}{Mar 2026 -- Jun 2026}{Team Leader (Team 5)}

\smallskip
\textbf{Summary.} YOLOv11-based object detection identifies four classes (Person, Hand, Hat, Product) on a frame-by-frame basis, and SORT/DeepSORT maintains per-worker Track IDs across frames. A GRU-based time-series action recognition model classifies four action types (Pick, Place, Working, Other), and Handling Time \& Cycle Time are derived from RoI entry/exit events. Reliability is secured via $\pm\Delta t$ time-window matching and track-level debouncing. These values are automatically substituted into the LOB formula and visualized through a real-time dashboard.

\smallskip
\textbf{Key Results.}
\begin{itemize}
  \item Detection: mAP@0.5 = 85.0\%, Precision = 87.6\%, Recall = 79.0\%, F1 = 83.0\%.
  \item LOB agreement with manual measurement: \textbf{95.0\%}.
  \item Enables automatic conversion of unstructured video into structured productivity metrics (LOB).
\end{itemize}

\cvsection{Government-Supported Projects}

\begin{itemize}
  \item \textbf{2026} \quad Manufacturing Robot Revitalization Project
  \item \textbf{2025} \quad Manufacturing AI Specialization Project
  \item \textbf{2024} \quad Digital Twin \& Safety Enhancement Project
  \item \textbf{2023} \quad Manufacturing Robot Plus Project
  \item \textbf{2022} \quad K-Smart Lighthouse Factory
  \item \textbf{2021} \quad Smart Factory Advancement Project
  \item \textbf{2020} \quad Smart Factory Foundation Project
\end{itemize}
{\small\color{body}\textit{All projects supported by the Ministry of SMEs and Startups (MSS), Republic of Korea.}}

\cvsection{Reviewed Literature}

{\small\color{body}\textit{Selected references reviewed by Team 5 during the capstone project on Video AI-based LOB analysis.}}

\begin{enumerate}\small
  \item YOLO-DS: Fine-Grained Feature Decoupling via Dual-Statistic Synergy Operator for Object Detection.
  \item Detection of Anomalous Behavior of Manufacturing Workers Using Deep Learning-Based Recognition of Human-Object Interaction.
  \item SMA-YOLO: A Multi-Scale Object Detection Algorithm for UAV Remote Sensing Images.
  \item YOLOv11: An Overview of the Key Architectural Enhancements.
  \item A Deep Context Learning-Based PCB Defect Detection Model with Anomalous Trend Alarming System.
  \item LiVOS: Light Video Object Segmentation with Gated Linear Matching.
  \item Towards Adaptive Human-Centric Video Anomaly Detection.
\end{enumerate}

\switchcolumn

%% ---- RIGHT COLUMN ----

\cvsection{My Life Philosophy}

\begin{quote}
``Continuous improvement is not a destination, but a way of thinking and living.''
\end{quote}

\cvsection{Research Outcomes}

\cvachievement{\faFileAlt}{Patent}{\textit{Real-time LOB Computation Program based on YOLO and GRU-driven Time-Series Action Recognition.}}

\divider

\cvachievement{\faCode}{Software Registration}{\textit{Real-time LOB Computation Program based on YOLO and GRU-driven Time-Series Action Recognition.}}

\divider

\cvachievement{\faBook}{Publication}{\textit{A Study on Worker Detection and Automated Line-of-Balance (LOB) Analysis in Manufacturing Packaging Lines Using YOLO-Based Video AI.}}

\cvsection{Most Proud of}

\cvachievement{\faTrophy}{Presidential Prize}{Awarded the Presidential Prize at the Manufacturing Innovation Awards for improving productivity through Smart Factory establishment.}

\divider

\cvachievement{\faIndustry}{8B KRW Cost Savings}{Realized 8 billion KRW in cost savings through DX and process innovation initiatives in FY2025.}

\divider

\cvachievement{\faChartLine}{30\% Productivity Gain}{Achieved a 30\% productivity increase and 20\% reduction in customer complaints across manufacturing operations.}

\cvsection{Strengths}

\cvtag{Smart Factory Planning}
\cvtag{AI/DX Transformation}\\
\cvtag{Process Optimization}

\divider\smallskip

\cvtag{Computer Vision}
\cvtag{YOLO / GRU}\\
\cvtag{Team Leadership}
\cvtag{Manufacturing Innovation}

\cvsection{Languages}

\cvskill{Korean}{5}
\divider
\cvskill{English}{4}

\cvsection{Education}

\cvevent{Graduate Studies}{Sungkyunkwan University}{}{}
Department of Smart Factory Convergence \\
\textit{Capstone Team Leader (Team 5)}

\cvsection{Contact}

\printinfo{\faEnvelope}{hala2517@gmail.com}[mailto:hala2517@gmail.com]
\smallskip
\printinfo{\faPhone}{+82-10-4621-4710}
\smallskip
\printinfo{\faGithub}{github.com/hala2517}[https://github.com/hala2517]
\smallskip
\printinfo{\faMapMarker*}{Eumseong-gun, Chungcheongbuk-do\\Republic of Korea}

\end{paracol}

\end{document}
